On the Minimum Core Mass for Giant Planet Formation through Kelvin-Helmholtz Contraction

### 2013-05-09 tex/draft/draft2.tex
slightly updated section 5

Standard static calculations of giant planet formation that consider planetesimal accretion as the main source of luminosity (e.g., \citealt{mizuno78}, \citealt{stevenson82}, \citealt{rafikov06}) assume that the atmosphere is at all times in a steady state at which the luminosity due to planetesimal accretion is fully radiated away by the atmosphere. The core and the atmosphere grow simultaneously, and the mass of the envelope is a function of the core mass. When the atmosphere mass becomes comparable to the mass of the solid core, hydrostatic balance no longer holds and runaway gas accretion commences. Therefore, for a set of disk and gas conditions, there is a maximum mass the core can have before the onset of unstable accretion: this is defined as the critical core mass. %a single value for the critical core mass $M_{\rm{crit}}$ is found, when the mass of the gaseous envelope is equal to the mass of the core. This is the maximum mass the core can have before unstable gas accretion commences.

In our model the atmosphere is no longer in steady state, because energy balance requires gas accretion, and the atmosphere contracts on a Kelvin-Helmholtz time scale. Figure \ref{fig:growthtime} shows the evolution of the atmosphere growth time with mass at several locations in our fiducial disk. In the early stages when $M_{\rm{atm}}$ is small, the envelope has a thin radiative zone with a high luminosity (see Figure \ref{fig:Ltplot}). As a result, the envelope initially grows quickly, i.e. on a short time scale, as shown in Figure \ref{fig:growthtime}. As the radiative zone becomes thicker, the luminosity decreases and growth is slowed down as a result. For our choice of parameters, we see that accretion is slowest for an atmosphere mass of $1-2 M_{\oplus}$. This is when the self-gravity of the atmosphere starts to matter; the envelope becomes massive enough for its energy to be large compared to the internal energy of the nebular gas. As a result, growth is continuously accelerated, and eventually runaway gas accretion settles in when the mass of the atmosphere becomes comparable to the core mass. Since growth is slowest long before $M_{\rm{atm}} \sim M_{\rm c}$, the estimate of the time to initiate runaway gas accretion is insensitive to the exact choice of crossover atmosphere mass to order of magnitude. We therefore choose the effective crossover mass, past which hydrostatic balance no longer holds, to be the minimum between $M_{\rm{c}}$ and the $M_{\rm{atm}}<M_{\rm c}$ at which our model becomes unphysical according to equation (\ref{eq:dti}), noting that both of these occur after the slow accretion phase for all our parameter choices. We define the \textit{crossover time} $t_{\rm{co}}$ as the time elapsed until runaway accretion commences according to the criteria above.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mt_profile.pdf}
%\vspace{-0.5in}
\caption{Instantaneous cooling time evolution with total mass at 10, 30 and 60 AU. Accretion is slowest at $M_{\mathrm{atm}} \sim 1-2 M_{\oplus}$.}
\label{fig:growthtime}
\end{figure}

@@

In this section we explore the effect of core mass on the atmosphere evolution time, for a fixed semi-major axis. We choose $a=10$ AU. Figure \ref{fig:tvsM} shows the crossover time behavior for a range of cores with masses between 1 and 10 $M_{\oplus}$. The envelope grows faster if the core is more massive, as it can bind a gaseous atmosphere quicker due to larger gravity. As such, for a fixed crossover time, e.g. the life timescale of the protoplanetary disk, there is a minimum core mass needed to form a planet within this time frame, which we defined above as the critical core mass. We defer the numerical estimates of the critical core mass to section \ref{critcore}.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.52\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/cumul_coolingtime_vs_Matm_10au_mu235.pdf}
%\vspace{-0.5in}
\caption{Time evolution as a function of atmosphere mass for a range of core masses. The circles mark the crossover time. A larger core mass results in a shorter crossover time.}
\label{fig:tvsM}
\end{figure}

@@

In what follows we explore how the crossover time is affected by the planet's location in the disk. The location only matters because it dictates the disk temperature and pressure (see equations (\ref{eq:diskb}) and (\ref{eq:Pd})). We therefore study the separate effects of disk temperature and pressure on the time evolution of the atmosphere. At a fixed distance in the disk $a=10$ AU and for a core mass $M_{\mathrm{c}}=5 M_{\oplus}$, we fix the disk temperature $T_{\rm{d}}$ at the value given by equation (\ref{eq:diskb}) and vary the disk pressure $P_{\rm{d}}$. We perform a similar analysis on the effect of disk temperature $T_{\rm{d}}$ on the crossover time by fixing the disk pressure at the value given by equation (\ref{eq:Pd}) and varying $T_{\rm{d}}$. The resulting time evolution is plotted in Figure \ref{fig:TPeffects}. For comparison, we also plot the results predicted by the analytic, non self-gravitating model described in section \ref{analytic}. However, we saw in equation (\ref{eq:tcoolan}) that the crossover time as predicted by the analytic results is too long; since we are investigating whether the analytic model predicts the correct scalings as opposed to the actual absolute results, when compared to the numerical model, we estimate the analytic crossover time as the time needed for the atmosphere mass to become a small fraction of the core mass, rather than equal to it: $M_{\rm{atm}}=f M_{\rm c}$. We use $f = 0.13$.

\begin{figure*}[tb]
\centering
\includegraphics[width=1.\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/TdPd_effect.pdf}
%\vspace{-0.5in}
\caption{Disk temperature and pressure effect on the crossover time $t_{\rm{co}}$. Gas accretion is faster for lower temperatures and higher pressures. The analytic scalings are plotted for comparison, for an effective crossover mass $M_{\rm{co}}$=f M_{\rm c} with $f=0.13$.}
\label{fig:TPeffects}
\end{figure*}

@@

An increase in disk temperature results in a longer crossover time, as a higher temperature causes an increase in opacity and hence a lower luminosity. The analytic model predicts $t_{\rm{co}} \propto T^{\beta+ 1/2}$ (see equation (\ref{eq:tcoolan})), where $\beta$ is the constant in the opacity law \ref{eq:opacitylaw}. For our choice of $\beta=2$, the crossover time is therefore strongly dependent on the opacity. Nevertheless, different opacity assumptions will result in a different scaling with temperature of $t_{\rm{co}}$. We notice a generally good agreement between our numerical results and the scaled analytic approximation in the left panel of Figure \ref{fig:TPeffects}. A factor of $\sim 3$ reduction in the disk temperature results in an decrease of the growth time by a factor of $\sim 30$. The atmosphere evolution is therefore strongly dependent on the temperature in the protoplanetary disk.

In contrast with the temperature effect, the crossover time decreases with disk pressure.  This effect can also be explained by the analytic model. From equations (\ref{eq:tcoolan}) and (\ref{eq:xi}), the crossover time is inversely proportional to the disk pressure. A higher disk pressure will therefore result in a shorter crossover time. Increasing the disk pressure by a factor of $\sim 100$ only reduces the crossover time by a factor of $\sim 2$. As such, the crossover time is only weakly dependent on the nebular pressure.

@@

In this work we build evolutionary atmosphere profiles assuming an ideal gas equation of state with constant mean molecular weight and adiabatic index. A realistic gas mixture, however, has variable adiabatic gradient and molecular weight, due to non-ideal effects and processes like dissociation or ionization. Future work will include real gas equation of state tables, and we expect quantitatively different results. In this study we analyze only the effect of the mean molecular weight of the nebular gas on the crossover time.   Specifically, we compare our standard model given by $\delad=2/7$ and $\mu=2.35$ with a model with the same adiabatic index but a different molecular mass, $\mu=2$ (i.e., purely molecular hydrogen). The result is shown in Figure \ref{fig:tvsMcomp}. We also plot the analytic results for comparison, using the same fractional mass scaling as in subsection \ref{TPeffects}, $f=0.13$, and notice that they are in good agreement with the numerical models. A lower mean molecular weight translates into a longer crossover time for the same core mass, since an atmosphere composed of heavier molecules is easier to bind.

\begin{figure}[h]
\centering
\includegraphics[width=0.48\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/coolingtime_vs_Mc_10au.pdf}
%\vspace{-0.5in}
\caption{The crossover time $t_{\rm{co}}$ for atmospheres with different mean molecular weight. A typical protoplanetary disk life time is plotted for comparison. The crossover time is larger for a lower $\mu$.}
\label{fig:tvsMcomp}
\end{figure}

We further investigate the effect of opacity reduction on the atmosphere evolution. We explore opacity laws in which the coefficient $\kappa_0$ from equation (\ref{eq:opacitylaw})  is reduced by factors of 10 and 100. The result is depicted in Figure \ref{fig:LtvsMopacity}. All things equal, a lower opacity increases he luminosity and hence speeds atmosphere growth by the same factor as the opacity reduction (see equations (\ref{eq:structd}) and (\ref{eq:delrad})).

 \begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/opacity_effect.pdf}
%\vspace{-0.5in}
\caption{Comparison between standard dust opacity and opacity reduced by factor of 10 and 100, respectively. Lower opacity accelerates atmosphere growth.}
\label{fig:LtvsMopacity}
\end{figure}

@@

In the previous subsections we explored the effect of disk and gas properties on the growth time of an atmosphere accreting around a protoplanetary core of fixed mass. The main question we address here is under what conditions the atmosphere can grow before the gas in the protoplanetary disk is dissipated. Specifically, we determine the minimum core mass that is necessary for a protoplanet to initiate runaway gas accretion within the disk lifetime, i.e. to have a crossover time equal to the disk life timescale. We  denoted this mass the \textit{critical core mass} in section \ref{Mct}.

Observations of protoplanetary disks show that they dissipate over a time scale of a few million years (e.g., \citealt{lagrange00}, \citealt{haisch01}, \citealt{goldreich04}). We adopt a disk life timescale of $\tau=3 $ Myrs and determine the critical core mass as a function of gas and disk conditions. The results are displayed in Figure \ref{fig:Mcvsa}.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mcrit_vs_a_3Myrs_new.pdf}
%\vspace{-0.5in}
\caption{The minimum core mass for an atmosphere to become critical within the lifetime of the disk $t \sim 3 Myrs$ as a function of semi-major axis, for different mean molecular weight of the nebular gas. The analytic results are plotted for comparison. The critical core mass is lower further out in the disk.}
\label{fig:Mcvsa}
\end{figure}

The critical core mass decreases as we move further away in the disk, primarily due to the fact the disk temperature is lower in the outer regions of the disk. As we showed in section \ref{TPeffects}, the atmosphere grows faster for lower temperatures, which offsets the need for a larger core mass. The critical core mass is larger for a lower mean molecular weight, consistent with the results derived in section \ref{Mct}. \textbf{Add explanation for analytic curve behavior --- need to chat about this with Andrew}. We also explore the opacity effect on the critical core mass. The results are shown in Figure \ref{fig:Mcritopacity} For an opacity, and therefore crossover time, reduced by an order of magnitude, the critical core mass is reduced by roughly a factor of 2.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mcrit_vs_a_3Myrs_opacity.pdf}
%\vspace{-0.5in}
\caption{Opacity effect on critical core mass. A factor of ten opacity reduction results in a critical core mass twice as small.}
\label{fig:Mcritopacity}
\end{figure}

>>>>

Standard static calculations of giant planet formation that consider planetesimal accretion as the main source of luminosity (e.g., \citealt{mizuno78}, \citealt{stevenson82}, \citealt{rafikov06}) assume that the atmosphere is at all times in a steady state at which the luminosity due to planetesimal accretion is fully radiated away by the atmosphere. The core and the atmosphere grow simultaneously, and the mass of the envelope is a function of the core mass. As the atmosphere mass becomes comparable to the mass of the solid core, hydrostatic balance no longer holds and runaway gas accretion commences. Therefore, for a set of disk and gas conditions, there is a maximum mass the core can have before the onset of unstable accretion: this is defined as the critical core mass. %a single value for the critical core mass $M_{\rm{crit}}$ is found, when the mass of the gaseous envelope is equal to the mass of the core. This is the maximum mass the core can have before unstable gas accretion commences.

In our model the atmosphere is no longer in steady state, because energy balance requires gas accretion, and the atmosphere contracts on a Kelvin-Helmholtz time scale. Figure \ref{fig:growthtime} shows the evolution of the atmosphere growth time with mass at several locations in our fiducial disk for a fixed core mass. In the early stages when $M_{\rm{atm}}$ is small, the envelope has a thin radiative zone and hence a high luminosity (see Figure \ref{fig:Ltplot}). As a result, the envelope initially grows quickly, as shown in Figure \ref{fig:growthtime}. As the radiative zone becomes thicker, the luminosity decreases and growth slows down. For our choice of parameters, we see that accretion is slowest for an atmosphere mass of $1-2 M_{\oplus}$. This is when the self-gravity of the atmosphere starts to matter; the envelope becomes massive enough for its energy to be large compared to the internal energy of the nebular gas. As a result, growth is continuously accelerated, and eventually runaway gas accretion settles in when the mass of the atmosphere becomes comparable to the core mass. Since growth is slowest before $M_{\rm{atm}} \sim M_{\rm c}$ for the cases that we tried, the estimate of the time to initiate runaway gas accretion is insensitive to the exact choice of crossover atmosphere mass to order of magnitude. We therefore choose the effective crossover mass, past which hydrostatic balance no longer holds, to be the minimum between $M_{\rm{c}}$ and the $M_{\rm{atm}}<M_{\rm c}$ at which our model becomes unphysical according to equation (\ref{eq:dti}), noting that both of these occur after the slow accretion phase for all our parameter choices. We define the \textit{crossover time} $t_{\rm{co}}$ as the time elapsed until the atmosphere mass becomes equal to the effective crossover mass as defined above, and runaway accretion commences.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mt_profile.pdf}
%\vspace{-0.5in}
\caption{Instantaneous growth time for the atmosphere of a planet with fixed core mass $M_{\rm c}=5 M_{\oplus}$ as a function of atmospheric mass, for a planet located at 10, 30 and 60 AU. Accretion is slowest before the mass of the atmosphere becomes comparable to the mass of the core. In this example, this happens at $M_{\mathrm{atm}} \sim 1-2 M_{\oplus}$.}
\label{fig:growthtime}
\end{figure}

@@

We begin by fixing the disk properties and generating atmosphere profiles for a set of fixed core masses. Figure \ref{fig:tvsM} shows the crossover time behavior for a range of cores with masses between 1 and 10 $M_{\oplus}$, at $a=10$ AU in our fiducial disk. The envelope grows faster if the core is more massive, as it can bind a gaseous atmosphere more quickly due to larger gravity. This can also be seen from the analytical results in equation (\ref{eq:tcoolan}). As such, for a fixed crossover time, e.g. the typical lifetime of the protoplanetary disk, there is a minimum core mass needed to form a planet within this time frame, which we defined above as the critical core mass. We defer numerical estimates of the critical core mass to section \ref{critcore}.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.52\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/cumul_coolingtime_vs_Matm_10au_mu235.pdf}
%\vspace{-0.5in}
\caption{We generate atmosphere profiles at $a=10$ AU for cores with fixed masses between $5 M_{\oplus}$ and $14 M_{\oplus}$. We plot the cumulative cooling time as a function of atmosphere mass. The circles mark the crossover time. A larger core mass results in a shorter crossover time.}
\label{fig:tvsM}
\end{figure}

@@

In what follows we explore how the crossover time is affected by the planet's location in the disk. The location only matters because it dictates the disk temperature (equation (\ref{eq:diskb})) and pressure (equation (\ref{eq:Pd})). We therefore study the separate effects of disk temperature and pressure on the time evolution of the atmosphere. At a fixed distance in the disk $a=10$ AU and for a core mass $M_{\mathrm{c}}=5 M_{\oplus}$, we fix the disk temperature $T_{\rm{d}}$ at the value given by equation (\ref{eq:diskb}) and vary the disk pressure $P_{\rm{d}}$. We perform a similar analysis on the effect of disk temperature $T_{\rm{d}}$ on the crossover time by fixing the disk pressure at the value given by equation (\ref{eq:Pd}) and varying $T_{\rm{d}}$. The resulting time evolution is plotted in Figure \ref{fig:TPeffects}. For comparison, we also plot the results predicted by the analytic, non self-gravitating model described in section \ref{analytic}. However, we saw in equation (\ref{eq:tcoolan}) that the crossover time as predicted by the analytic results is too long. Here we are investigating whether the analytic model predicts the correct scalings as opposed to the actual absolute results, when compared to the numerical model. We therefore estimate the analytic crossover time as the time needed for the atmosphere to reach an effective crossover mass $M_{\rm{atm}}=f M_{\rm c}$, where $f = 0.13$.

\begin{figure*}[tb]
\centering
\includegraphics[width=1.\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/TdPd_effect.pdf}
%\vspace{-0.5in}
\caption{Left panel: crossover time as a function of disk temperature for fixed disk pressure and a core of fixed mass $M_{\rm c}=5 M_{\oplus}$. Right panel: crossover time as a function of disk pressure for fixed disk temperature and a core of fixed mass  $M_{\rm c}=5 M_{\oplus}$. The analytic scalings are plotted for comparison, for an effective crossover mass $M_{\rm{co}}=f M_{\rm c}$ with $f=0.13$. Gas accretion is faster for lower temperatures and higher pressures.} 
\label{fig:TPeffects}
\end{figure*}

@@

An increase in disk temperature results in a longer crossover time, as a higher temperature causes an increase in opacity and hence a lower luminosity. The analytic model predicts $t_{\rm{co}} \propto T^{\beta+ 1/2}$ (see equation (\ref{eq:tcoolan})), where $\beta$ is the constant in the opacity law (\ref{eq:opacitylaw}). For our choice of $\beta=2$, the crossover time is therefore strongly dependent on the opacity. Different opacity assumptions will result in a different scaling with temperature of $t_{\rm{co}}$. We notice a generally good agreement between our numerical results and the scaled analytic approximation in the left panel of Figure \ref{fig:TPeffects}. A factor of $\sim 3$ reduction in the disk temperature results in an decrease of the growth time by a factor of $\sim 30$. The atmosphere evolution is therefore strongly dependent on the temperature in the protoplanetary disk.

An increase in disk pressure will decrease the crossover time. This effect can also be explained by the analytic model. From equations (\ref{eq:tcoolan}) and (\ref{eq:xi}), the crossover time is inversely proportional to the disk pressure. A higher disk pressure will therefore result in a shorter crossover time. Increasing the disk pressure by a factor of $\sim 100$ only reduces the crossover time by a factor of $\sim 2$. As such, the crossover time is only weakly dependent on the nebular pressure.

@@

In this work we build evolutionary atmosphere profiles assuming an ideal gas equation of state with constant mean molecular weight and adiabatic index. A realistic gas mixture, however, has variable adiabatic gradient and molecular weight, due to non-ideal effects and processes like dissociation or ionization. Future work will include real gas equation of state tables, and we expect quantitatively different results. In this study we analyze only the effect of the mean molecular weight of the nebular gas on the crossover time.   In Figure \ref{fig:tvsMcomp}, we compare our standard model given by $\delad=2/7$ and $\mu=2.35$ with a model with the same adiabatic index but a different molecular mass, $\mu=2$ (i.e., purely molecular hydrogen). We also plot the analytic results for comparison, using the same fractional mass scaling as in subsection \ref{TPeffects}, $f=0.13$, and notice that they are in good agreement with the numerical models. A lower mean molecular weight translates into a longer crossover time for the same core mass, since an atmosphere composed of heavier molecules is easier to bind.

\begin{figure}[h]
\centering
\includegraphics[width=0.48\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/coolingtime_vs_Mc_10au.pdf}
%\vspace{-0.5in}
\caption{The crossover time $t_{\rm{co}}$ as a function of core mass at $a=10$ AU, for atmospheres with different mean molecular weight. A typical protoplanetary disk life time $t=3$ Myrs is plotted for comparison. The crossover time is larger for a lower mean molecular weight.}
\label{fig:tvsMcomp}
\end{figure}

A decrease in opacity reduces the number of steps that photons need to diffuse (since it increases their mean free path), resulting in a higher luminosity. In Figure \ref{fig:LtvsMopacity}, we explore opacity laws in which the coefficient $\kappa_0$ from equation (\ref{eq:opacitylaw}) is reduced by factors of 10 and 100. All things equal, a lower opacity increases the luminosity and hence speeds atmosphere growth by the same factor as the opacity reduction (see equations (\ref{eq:structd}) and (\ref{eq:delrad})).

 \begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/opacity_effect.pdf}
%\vspace{-0.5in}
\caption{Luminosity and cooling time evolution with total atmosphere mass for planets of fixed core mass $M_{\rm c}=5 M_{\oplus}$ and located at $a=10$ AU, for different opacities. The standard dust opacity is reduced by factors of 10 and 100, respectively. A lower opacity accelerates atmosphere growth.}
\label{fig:LtvsMopacity}
\end{figure}

@@

We can now combine the results obtained in sections \ref{Mct}, \ref{TPeffects} and \ref{muopacity} to determine the minimum core mass necessary for a protoplanet to initiate runaways gas accretion within the disk lifetime, i.e. to have a crossover time equal to the disk life timescale. We  denote this mass the \textit{critical core mass}.

%In the previous subsections we explored the effect of disk and gas properties on the growth time of an atmosphere accreting around a protoplanetary core of fixed mass. The main question we address here is under what conditions the atmosphere can grow before the gas in the protoplanetary disk is dissipated. Specifically, we determine the minimum core mass that is necessary for a protoplanet to initiate runaway gas accretion within the disk lifetime, i.e. to have a crossover time equal to the disk life timescale. We  denoted this mass the \textit{critical core mass} in section \ref{Mct}.

Observations of protoplanetary disks show that they dissipate over a time scale of a few million years (e.g., \citealt{lagrange00}, \citealt{haisch01}, \citealt{goldreich04}). We adopt a disk life timescale of $\tau=3 $ Myrs and determine the critical core mass as a function of gas and disk conditions.

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mcrit_vs_a_3Myrs_new.pdf}
%\vspace{-0.5in}
\caption{The minimum core mass for an atmosphere to initiate runaway gas accretion within the lifetime of the disk $t \sim 3 Myrs$ as a function of semi-major axis, for different mean molecular weight of the nebular gas. The analytic results are plotted for comparison. The critical core mass is lower further out in the disk.}
\label{fig:Mcvsa}
\end{figure}

 In Figure \ref{fig:Mcvsa}, we see that the critical core mass decreases as we move further away in the disk, primarily due to the fact the disk temperature is lower in the outer regions of the disk. As we showed in section \ref{TPeffects}, the atmosphere grows faster for lower temperatures, which offsets the need for a larger core mass. The critical core mass is larger for a lower mean molecular weight, consistent with the results derived in section \ref{Mct}. \textbf{Add explanation for analytic curve behavior --- need to chat about this with Andrew}. We also explore the opacity effect on the critical core mass in Figure \ref{fig:Mcritopacity} For an opacity, and therefore crossover time, reduced by an order of magnitude, the critical core mass is reduced by roughly a factor of 2.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.5\textwidth]{../../figs/ModelAtmospheres/RadSelfGravPoly/PaperFigs/Mcrit_vs_a_3Myrs_opacity.pdf}
%\vspace{-0.5in}
\caption{Critical core mass as a function of semi-major axis for different opacities. A factor of ten opacity reduction results in a critical core mass twice as small.}
\label{fig:Mcritopacity}
\end{figure}
